---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# matchedcc

<!-- badges: start -->
[![R-CMD-check](https://github.com/simpar1471/matchedcc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simpar1471/matchedcc/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/matchedcc)](https://CRAN.R-project.org/package=matchedcc)
<!-- badges: end -->

The aim of matchedcc is to provide epidemiologists using R with Stata-like
analysis of matched case-control data. This package has two functions, `mcc()`
and `mcci()`, which are direct analogues of Stata's own `mcc` and `mcci`
commands.

## Installation

You can install the development version of matchedcc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("simpar1471/matchedcc")
```

## Examples

The functions in matchedcc are easy to use. To demonstrate their use, we will
use the `mccxmpl` dataset, which is included in matchedcc. This dataset has two
columns - `cases` and `controls`. In this dataset, cases had experienced a heart
attack, and cases and controls were matched accordingly. Each column has only
`1` or `0` values, which describe whether a case or control encountered our
exposure - in this case, drinking >6 cups of coffee per day.

```{r show_data}
library(matchedcc)
head(matchedcc::mccxmpl)
```

### Vector input

The `mcc()` function will take vectors of `1`s and `0`s and use these to run a
matched case control analysis:

```{r example_vec}
mcc(cases = matchedcc::mccxmpl$case, controls = matchedcc::mccxmpl$control)
```

### 2x2 table input

The `mcc()` function can also accept a 2x2 table with matched case-control data,
provided it is in the following format:

| Cases     | Controls |           |
|-----------|----------|-----------|
|           | Exposed  | Unexposed |
| Exposed   | a        | b         |
| Unexposed | c        | d         |

```{r example_tbl}
mcc_table <- table(matchedcc::mccxmpl$control,
                   matchedcc::mccxmpl$case)
mcc(table = mcc_table)
```

### 'Immediate' input

Last but not least, if you have cell counts from a 2x2 table, you can provide
individual cell counts to `mcci()`:

```{r example_imm}
mcci(a = 8, b = 8, c = 3, d = 8)
```

## Validation against Stata

The package is validated against Stata's own outputs, using 1000 randomly
generated `mcci` runs from Stata. The code to generate these can be seen in
`/tests/testdata/run-stata-mcc.R`.

## Citation

Parker S (2024). _matchedcc: Stata-like matched case-control analysis_.
<https://github.com/lshtm-gigs/gigs/>.
