---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# matchedcc

<!-- badges: start -->
[![R-CMD-check](https://github.com/simpar1471/matchedcc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simpar1471/matchedcc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The aim of matchedcc is to provide epidemiologists using R with Stata-like
analysis of matched case-control data. This package has two functions, `mcc()`
and `mcci()`, which are direct analogues of Stata's own `mcc` and `mcci`
commands.

## Installation

You can install the development version of matchedcc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("simpar1471/matchedcc")
```

## Example


```{r example}
library(matchedcc)
matchedcc::mccxmpl
```

## Citation

Parker S (2024). _matchedcc: Stata-like matched case-control analysis_.
<https://github.com/lshtm-gigs/gigs/>.